\documentclass[]{article}

\usepackage{amsmath, amssymb}

%opening
\title{Fourier Transform}
\author{}

\begin{document}

\maketitle

\section{Fourier Transform}

The Fourier transform is a powerful tool used in signal decomposition, solving partial differential equations, and quantum mechanics. It decomposes a function into its constituent frequencies, providing a bridge between the time (or spatial) domain and the frequency domain.

In this article, the Fourier Transform is defined as
\[\mathcal{F}\{f(t)\}  = \frac{1}{\sqrt{2\pi}}\int_{-\infty}^{\infty} f(t)e^{-i\omega t}\,dt\]
and the inverse Fourier Transform is:
\[\mathcal{F}^{-1}\{F(\omega)\}  = \frac{1}{\sqrt{2\pi}}\int_{-\infty}^{\infty} F(\omega)e^{i\omega t}\,d\omega\]

By definition, the inverse of a function's transform should recover the original function. Then:
\[f(t) = \mathcal{F}^{-1} \{\mathcal{F}\{f(t)\}\}  = \frac{1}{2\pi}\int_{-\infty}^{\infty} \left(\int_{-\infty}^{\infty}
f(t')e^{-i\omega t'}\,dt'\right)e ^{i\omega t}\,d\omega\]
Combining the integrals and interchanging the order of integration,
\[f(t)  =\frac{1}{2\pi} \int_{-\infty}^{\infty} \int_{-\infty}^{\infty}
f(t')e^{-i \omega(t'-t)}  \,d\omega\, dt' \]
Since $f(t')$ behaves like a constant with respect to the $\omega$ integration:
\[f(t)  = \int_{-\infty}^{\infty} f(t')\left(\frac{1}{2\pi}\int_{-\infty}^{\infty}
e^{-i \omega(t'-t)}  \,d\omega\right) dt' \]
The inner integral is a function of $t'-t$. We define:
\[\delta(\tau) = \frac{1}{2\pi}\int_{-\infty}^{\infty}
e^{-i \omega \tau}  \,d\omega\]
However, this integral does not converge in the classical sense. When $\tau \neq 0$, the integrand oscillates and the integral evaluates to $0$. When $\tau = 0$, the integrand is $1$ everywhere, and the integral diverges. So how can we justify this object as a meaningful mathematical entity?

\section{Distribution}

The justification of $\delta(\tau)$ is through the theory of \textit{distributions} (also called generalized functions). Rather than asking what $\delta$ \textit{is} as a function, we ask what $\delta$ \textit{does} when paired with a test function $f$. From the analysis above, $\delta$ must pick out the value of $f$ at $0$ in order for the definition of the Fourier transform to remain consistent:
\[f(t)  = \int_{-\infty}^{\infty} f(t') \,\delta(t'-t)\, dt' \]

More generally, even innocent-looking functions such as $\sin(x)$ and $\cos(x)$ are not classically Fourier-transformable, since their integrals do not converge absolutely. Taking inspiration from the delta function, we define a distribution $\Phi$ acting on a test function $f$ via the pairing:
\[F(t)= \langle \Phi(x,t),\, f(x) \rangle = \int_{-\infty}^{\infty} \Phi(x,t)\,f(x)\,dx\]
Here we assume that $f(x)$ belongs to a suitable space of test functions (e.g.\ the Schwartz space $\mathcal{S}$), which ensures absolute convergence. Now, consider what happens when we apply the Fourier transform in the distributional sense:
\[\langle \Phi,\,\mathcal{F}^{-1}f \rangle = \int_{-\infty}^{\infty} \Phi(x,t) \int_{-\infty}^{\infty}f(\omega)\,e^{i\omega x}\, d\omega\, dx\] 

\subsection{Example: Fourier Transform of a Constant}

As a concrete application, consider $f(t) = 1$. Classically, $\int_{-\infty}^{\infty} e^{-i\omega t}\,dt$ diverges. However, in the distributional sense:
\[\mathcal{F}\{1\} = \sqrt{2\pi}\,\delta(\omega)\]
This can be verified by checking the pairing with any test function $g(\omega)$:
\[\langle \mathcal{F}\{1\},\, g \rangle = \int_{-\infty}^{\infty} \sqrt{2\pi}\,\delta(\omega)\,g(\omega)\,d\omega = \sqrt{2\pi}\,g(0)\]
which is exactly what the formal computation yields.

\subsection{Example: Fourier Transform of Trigonometric Functions}

Similarly, using Euler's formula $\cos(\omega_0 t) = \frac{1}{2}(e^{i\omega_0 t} + e^{-i\omega_0 t})$, one obtains:
\[\mathcal{F}\{\cos(\omega_0 t)\} = \sqrt{\frac{\pi}{2}}\left[\delta(\omega - \omega_0) + \delta(\omega + \omega_0)\right]\]
and likewise:
\[\mathcal{F}\{\sin(\omega_0 t)\} = i\sqrt{\frac{\pi}{2}}\left[\delta(\omega + \omega_0) - \delta(\omega - \omega_0)\right]\]
These results confirm that a pure sinusoid in the time domain corresponds to sharp spikes (delta functions) at the associated frequencies in the frequency domain.

\end{document}
