\documentclass[]{article}
\usepackage{amsmath}
%opening
\title{Energy and Momentum}
\author{}

\begin{document}

\maketitle
\section{Work and Energy}
The two words can be used interchangeably, each came from an unique understanding, while they are describing the same situation. These concepts are often used when the problem gets too complicated to come up with an explicit formula for  

\subsection{Definition}
	$$\text{Work done by } F = \vec{F} \cdot \vec{distance}$$
	In work done by conservative forces, the work done is recoverable. Or it can be thought as the potential energy that is the consequence of the work done by such forces.
	When work is done by non-conservative force, it is not recoverable and can be thought to turned into heat. 

	Because work being done by conservative forces are turned into potential energies, it can be thought as the energy of the system remain the same when work is done by conservative forces. The energy of the system can only be changed by non-conservative or external forces.
	
	In summary,
	$$\Delta E = 0 \text{ When the forces are all conservative}$$
	$$\Delta E = W_{NC} \text{ When non-conservative forces are present}$$ 
\section{Formulas}	
	\subsection{Friction}
	When two surfaces are rubbing each other, they will get heat up very easily. Therefore, the work done by friction is transferred into heat energy, making the friction force a non-conservative force. As a non-conservative force, work done by friction is dependent to the path it takes. 
	$$W_{fr} = F_{fr}\cdot \Delta x = \mu F_N \cdot \Delta x$$

	\subsection{Kinetic Energy}
	$$\Delta KE = m \frac{v_f^2 - v^2_i}{2}$$
	$$KE = m\frac{v^2}{2}$$

	We will only derive the $1$D scenario for the sake of understanding. 
	
	Because in classical physics, mass of an object doesn't change, $m$ remain constant.
	$F$ is a constant force.
	
	We will use $W_F$ to denote the work done by F.
	
	$\Delta x$ will represent  the change in distance.
	$$W_F = F \cdot \Delta x$$
	$$W_F = m (a \cdot \Delta x)$$
	Recall in kinematics, $v_f^2 = v^2_i + 2a\Delta x$
	$$v_f^2 - v^2_i = 2a\Delta x$$
	
	$$\frac{v_f^2 - v^2_i}{2} = a\Delta x$$
	So replace $a\Delta x$ into the original expression.
	$$W_F = m \frac{v_f^2 - v^2_i}{2}$$
	Assuming that a particle traveled from $A$ to $B$ with constant acceleration $a_1$ and from $B$ to $C$ with acceleration $a_2$. To calculate the work done from $A$ to $C$, we can add the work done in the first portion and the second portion.
	
	$$W_{AB} = m\frac{v_A^2 -v_B^2}{2}$$
	$$W_{BC} = m\frac{v_B^2 -v_C^2}{2}$$ 
	$$W_{AC} = W_{AB} + W_{BC} = m\frac{v_A^2 -v_C^2}{2}$$
	So the original expression holds when $a$ is not a constant term, or in other words when $F$ is not a constant force. 
	\subsection{Potential Energy}
		\subsubsection{Spring}
			By Hooke's law, 
			$$F = -k (x-x_0) = -k\Delta x$$
			Since it is a linear graph, use the formula for area of an triangle and get:
				$$PE = \frac{k\Delta x^2}{21}$$	

		
\section{Momentum}
$$L = mv$$
Assuming you are at an inertial frame of reference, an object's momentum relative to you is $mv$. A change in an object's momentum is:
$$\Delta L = m \Delta v$$
A change in momentum must be caused by an outside force because of the second equation in kinematics ($\Delta v = \Sigma a\Delta t$).

$$\Delta L = m\Delta v$$
$$\Delta L = m\Sigma a \Delta t$$
$$\Delta L = \Sigma m a \Delta t$$
$$\Delta L = \Sigma F \Delta t$$
Therefore, momentum is an alternate way of representing Newton's third law. Without outside forces, F will be $0$ (Newton's Third law) making the change of momentum $0$. 
 

\section{Collisions}
\subsubsection{Elastic}
Elastic means that two objects does NOT stick together after the collision. A complete elastic collisions are those in which both kinetic energy and momentum are conserved. For a collision between two bodies labeled 1 and 2, the following two equations describe an elastic collision:

$$E = \frac{1}{2} m_1 |\mathbf{v}_{1i}|^2 + \frac{1}{2} m_2 |\mathbf{v}_{2i}|^2 = \frac{1}{2} m_1 |\mathbf{v}_{1f}|^2 + \frac{1}{2} m_2 |\mathbf{v}_{2f}|^2$$

\begin{enumerate}
	\item $|\mathbf{v}_{1i}|$ and $|\mathbf{v}_{2i}|$ are the magnitudes of the initial velocities of bodies 1 and 2,

	\item $|\mathbf{v}_{1f}|$ and $|\mathbf{v}_{2f}|$ are the magnitudes of the final velocities of bodies 1 and 2 after collision.

\end{enumerate}
$$L = m_1 \mathbf{v}_{1i} + m_2 \mathbf{v}_{2i} = m_1 \mathbf{v}_{1f} + m_2 \mathbf{v}_{2f}$$

\begin{enumerate}
\item $m_1$ and $m_2$ are the masses of bodies 1 and 2 respectively,

\item $v_{1i}$ and $v_{2i}$ are the initial velocities of bodies 1 and 2,

\item $v_{1f}$ and $v_{2f}$ are the final velocities of bodies 1 and 2 after collision.
  
\end{enumerate}
\subsubsection{Inelastic}
Inelastic means that the two object stick together after the collision. In an inelastic collision, momentum is conserved but kinetic energy is not. Instead, some of the kinetic energy is converted into potential energy in holding the body together. (converted into heat, sound, or movement is also acceptable)
$$m_1 \mathbf{v}_{1i} + m_2 \mathbf{v}_{2i} = (m_1 +m_2)\mathbf{v}_{f}$$
When a body is split into two or more separate parts, it is also an type of inelastic collision called reverse inelastic collision. 
$$(m_1 +m_2)\mathbf{v}_{i} = m_1 \mathbf{v}_{1f} + m_2 \mathbf{v}_{2f} $$

To understand why energy is not conserved conceptually, we can use reverse inelastic collision as an example. When the observer is traveling at the same speed as $\mathbf{v}_{i}$, the object will remain static to the observer. At some point in time, the observer will see the parts of the object traveling at a speed of $\mathbf{v}_{1f} -\mathbf{v}_{i}$ and  $\mathbf{v}_{2f} -\mathbf{v}_{i}$ away from the observer. So the kinetic energy went from $0$ relative to the observe to $\frac{1}{2} m_1(\mathbf{v}_{1f} -\mathbf{v}_{i})^2 + \frac{1}{2} m_2 (\mathbf{v}_{2f} -\mathbf{v}_{i})^2$. Therefore the energy is not conserved.
$$\frac{1}{2} m_1 |\mathbf{v}_{1i}|^2 + \frac{1}{2} m_2 |\mathbf{v}_{2i}|^2 \neq \frac{1}{2} m_1 |\mathbf{v}_{1f}|^2 + \frac{1}{2} m_2 |\mathbf{v}_{2f}|^2$$


\section{Question}
\begin{enumerate}
	\item Emma carried her pet gold fish to walk from her parents' house to her grandparents' house, she walked for 2 miles to get to her destination. Why did she not do any work on the gold fish even though she felt really tired after the walk. (Do not use definition, answer it conceptually, and with full understanding of the concept)
\end{enumerate}


\end{document}
